Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-10 minimax.tex
minimal changes introduction

\section{Related Work}
\label{sec:related}
In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known). One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules, determining lower and upper bounds; they showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated.

>>>>

\paragraph{Related Work}
\label{sec:related}
In the context of social choice, several authors have been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences (assuming that the voting rule is known). One early work is  by \Citet{Conitzer2005} who studied the complexity of communication, using different voting rules, determining lower and upper bounds; they showed that, in the worst case, the agents should send their complete set of preference for several rules.
